Golf-Sport: Managing Operations \\ A Case Study in Optimization

### 2018-04-05 Paper.tex
author added
Margin Change
outline order
changed order
assump

\documentclass{article}
\title{Golf-Sport:  Managing Operations \\ A Case Study in Optimization}
\date{May 8, 2018}
\author{John D. Bulger \& xxxxxx, Valparaiso University}
%Add in Matt
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\newpage
	\pagenumbering{arabic}
\section{Introduction}
This problem examines a manufacturing optimization case........
\section{Description of Problem}
This is where we describe what the problem we are trying to solve is
\section{Background and Prior Work}
Here is a good spot to insertour necessary references.  We can evaluate solutions of similar problems
\section{Mathematical Formulation \& Model}
\subsection{Assumptions}
Here we add assumptions about 2 month not going concern, minimization of inventory, selling all of per 1 and using period 3 for carryover
\subsection{Variables}
List our variables and indices, maybe in a table if i can figure out how to do it
\subsection{Objective}
Here we put in our objective function and explain the goal behind it
\subsection{Constraints}
Here we list all constraints in with an explanation surrounding each
\subsection{Heuristics}
Just kidding, this problem is not big enough for any heuristics
\section{Implementation}
\subsection{Hardware \& Software}
Problem was solved using MATLAB R2017B  It was run on a computer.....
\subsection{Coding}
%Maybe insert a page of pseudocode here???????
Code
\subsection{Algorithm}
Run as an IP using optimproblem, which is essentially an interior points method of solution.  Will run an LP to examine solutions
\section{Solution}
Explain results, compare to linear relaxation of the problem
\par
maybe insert a section with a graph or chart to visualize production
\section{Further Analysis}
Conduct range sensitivity, examine extra problems in case study
\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Evaluate our approach, suggest changes in future.  EFFICIENCY
\subsection{Company Approach}
Discuss optimized solution, range sensitivity, business suggestions
	\newpage
	\pagenumbering{gobble}
	\begin{thebibliography}{9}
\bibitem{bulger88}

>>>>

\documentclass{article}
\title{Golf-Sport:  Managing Operations \\ A Case Study in Optimization}
\date{May 8, 2018}
\author{John D. Bulger \& Matthew Hess, Valparaiso University}
\usepackage[margin=1in]{geometry}
\begin{document}
	\pagenumbering{gobble}
	\maketitle
	\newpage
	\pagenumbering{arabic}
\section{Introduction}
This problem examines a manufacturing optimization case........
\section{Background and Prior Work}
Here is a good spot to insertour necessary references.  We can evaluate solutions of similar problems
\section{Description of Problem}
Golf-Sport is a golfclub manufacturing company with three plants in Arizona.  Each plant has an attached retail store and is treated as its
only supplier.  Each location has predicted minimum and maximum sales of each item type per period.  The goal of this optimization is to maximize profit over a two-month period by determining the optimal number of each product to make
at each location.  In this problem, two types of constraints exist:  local \& global.  Local constraints are unique to each plant/store
 combination, while the global constraints refer to company-wide resources.
\section{Mathematical Formulation \& Model}
\subsection{Assumptions}
Two main assumptions were made in order to create an effective model for this problem.  First, this model represents the company's production as if it were not a 
going-concern.  The model is constructed to optimize profit over two months, thereby not building up any additional inventory for carryover into 
a third month.  By default, the model will not have any inventory left at the end of the second month.  If further information were to arise along with 
a modeling need for a third month, this could be accomplished by expanding the current model. \par
The second assumption used is the carryover of graphite stock between months.  Advertising and graphite allotments are companywide in this problem, and 
it is clearly stated that the amount of money earmarked for advertising each month will not carryover into the next month.  Graphite seems to have no such restriction, so 
it appears reasonable to incorporate the possibility of carryover of graphite stock.
\subsection{Variables}
List our variables and indices, maybe in a table if i can figure out how to do it
\subsection{Objective}
Here we put in our objective function and explain the goal behind it
\subsection{Constraints}
Here we list all constraints in with an explanation surrounding each
\subsection{Heuristics}
Just kidding, this problem is not big enough for any heuristics
\section{Implementation}
\subsection{Hardware \& Software}
Problem was solved using MATLAB R2017B  It was run on a computer.....
\subsection{Coding}
%Maybe insert a page of pseudocode here???????
Code
\subsection{Algorithm}
Run as an IP using optimproblem, which is essentially an interior points method of solution.  Will run an LP to examine solutions
\section{Solution}
Explain results, compare to linear relaxation of the problem
\par
maybe insert a section with a graph or chart to visualize production
\section{Further Analysis}
Conduct range sensitivity, examine extra problems in case study
\section{Conclusions \& Implications}
\subsection{Mathematical Approach}
Evaluate our approach, suggest changes in future.  EFFICIENCY
\subsection{Company Approach}
Discuss optimized solution, range sensitivity, business suggestions
	\newpage
	\pagenumbering{gobble}
	\begin{thebibliography}{9}
\bibitem{bulger88}
